Exploratory Plots

### 2020-06-09 exploratory/2020/README.Rmd

# Fitting datasets to a reference database vs _de novo_ clustering
```{r functions}
relevel_method <- function(df) {
  df %>%
    mutate(method = fct_relevel(method, c("open", "closed", "de_novo")))
}
plot_jitter <- function(.df, ...) {
  .df %>% 
    ggplot(aes(...)) +
    geom_jitter() +
    scale_color_manual(values=dataset_colors)
}
```

```{r fit_db_sensspec}
sensspec <- read_tsv(here('subworkflows/2_fit_reference_db/results/sensspec.txt')) %>% 
  relevel_method()
sensspec %>% 
  group_by(dataset, method) %>% 
  plot_jitter(x = method, y = mcc, color = dataset) +
  ylim(0, 1)
```

```{r fit_db_benchmarks}
benchmarks <- read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.txt')) %>% 
  relevel_method
benchmarks %>% 
  group_by(dataset, method) %>% 
  plot_jitter(x = method, y = s, color = dataset) +
  labs(y='seconds')
```

```{r fit_db_input_size}

```

```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/2_fit_reference_db/results/fraction_reads_mapped.txt'))
fractions %>% 
  plot_jitter(x=dataset, y=fraction_mapped, color=dataset) +
  ylim(0, 1)
```

>>>>

# Fitting datasets to a reference database vs _de novo_ clustering
```{r functions}
relevel_method <- function(df) {
  df %>%
    mutate(method = fct_relevel(method, c("open", "closed", "de_novo")))
}
```

```{r fit_db_sensspec}
sensspec <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/sensspec.tsv')) %>%
  relevel_method()
sensspec %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = mcc, color = dataset)) +
  geom_jitter(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  ylim(0, 1) +
  facet_wrap("ref") 
```

```{r fit_db_benchmarks, warning=FALSE}
benchmarks <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.tsv')) %>%
  relevel_method
benchmarks %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = s, color = dataset)) +
  geom_boxplot() +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("ref") +
  labs(y = 'seconds')
```

```{r fit_db_input_size}
input_sizes <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/input_sizes.tsv'))
```

Only for closed-reference OptiFit

```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/2_fit_reference_db/results/fraction_reads_mapped.tsv'))
fractions %>% 
  ggplot(aes(x=dataset, y=fraction_mapped, color=dataset)) +
  geom_jitter(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("ref") +
  ylim(0, 1)
```
